\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}

\bibitem{Qx1}James H. Stock & Mark W. Watson, 2008.
"Phillips curve inflation forecasts," Conference Series ; [Proceedings], Federal Reserve Bank of Boston.

\bibitem{Qx2}Chakraborty, Chiranjit & Joseph, Andreas, 2017.
"Machine learning at central banks,"
Bank of England working papers 674, Bank of England.

\bibitem{Qx3}Garcia, Márcio G.P. & Medeiros, Marcelo C. & Vasconcelos, Gabriel F.R., 2017.
"Real-time inflation forecasting with high-dimensional models: The case of Brazil," International Journal of Forecasting, Elsevier, vol. 33(3), pages 679-693.

\bibitem{Qx4}Clements, Michael P. & Hendry, David F. (ed.), 2011.
"The Oxford Handbook of Economic Forecasting," OUP Catalogue,
Oxford University Press, number 9780195398649, April.
\bibitem{Qx5}Stock, James H. & Watson, Mark, 2011.
"Dynamic Factor Models,"
Scholarly Articles 28469541, Harvard University Department of Economics.

\bibitem{Qx7} E. F. Fama, “\Term-structure forecasts of interest rates, inflation and real returns,” Journal of Monetary Economics, vol. 25, no. 1, pp. 59–76, 1990.

\bibitem{Qx8} A. Ang, G. Bekaert, and M. Wei, “Do macro variables, asset markets, or surveys forecast inflation better?” Journal of Monetary Economics, vol. 54, pp. 1163–1212, 2007

\bibitem{Qx9} K. Hubrich, “Forecasting euro area inflation: does aggregating forecasts by HICP component improve forecast accuracy?” International Journal of Forecasting, vol. 21, no. 1, pp. 119–136, 2005.


\bibitem{Qx10} A. D’Agostino and P. Surico, “A century of inflation forcasts,” The Review of Economics and Statistics, vol. 94, no. 4, pp. 1097–1106, 2012.


\bibitem{Qx11} S. McKnight, A. Mihailov, and F. Rumler, “Inflation forecasting using the new keynesian Phillips curve with a time-varying trend,” Economic Modelling, vol. 87, pp. 383–393, 2020.


\bibitem{Qx12} C. S. Bos, P. H. Franses, and M. Ooms, “Inflation, forecast intervals and long memory regression models,” International Journal of Forecasting, vol. 18, pp. 243–264, 2002.



\bibitem{Qx13} A. Barnett, H. Mumtaz, and K. Theodoridis, “Forecasting UK GDP growth and inflation under structural change. A comparison of models with time-varying parameters,” International Journal of Forecasting, vol. 30, no. 1, pp. 129–143, 2014.



\bibitem{Qx14} S. Eickmeier, W. Lemke, and M. Marcellino, “Classical time varying factor-augmented vector auto-regressive models-estimation, forecasting and structural analysis,” Journal of the Royal Statistical Society: Series A, vol. 178, no. 3, pp. 493–533, 2015.




\bibitem{Qx15} A. Krizhevsky, I. Sutskever, and G. E. Hinton, “Imagenet classification with deep convolutional neural networks,” Proceedings of the NIPS, vol. 2, pp. 1096–1105, 2012.



\bibitem{Qx16} J. T. Connor, R. D. Martin, and L. E. Atlas, “Recurrent neural networks and robust time series prediction,” IEEE Transactions on Neural Networks, vol. 5, no. 2, pp. 240–254, 1994.




\bibitem{Qx17} M. M. Najafabadi, F. Villanustre, T. M. Khoshgoftaar, N. Seliya, R. Wald, and E. Muharemagic, “Deep learning applications and challenges in big data analytics,” Journal of Big Data, vol. 2, no. 1, pp. 1–21, 2015.



\bibitem{Qx18} S. Moshiri and N. Cameron, “Neural network versus econometric models in forecasting inflation,” Journal of Forecasting, vol. 19, no. 3, pp. 201–217, 2000.

\bibitem{Qx19} Data Source: https://data.worldbank.org/country/united-kingdom?view=chart

\bibitem{Qx20} Error : https://stackoverflow.com/

\bibitem{Qx21} Python Lib: https://docs.python.org/3/

\bibitem{Qx22} Google Search

\end{thebibliography}
